---
title: "LoViMAB Workflow Summary"
---

# Summary

This report is based on results generated with the LoViMAB v1.0.0 pipeline. WORK IN PROGRESS!!!

## Run Time and Resource Usage

This table shows the average resource usage for key processes across all samples.

```{r}
#| label: tbl-benchmark
#| tbl-cap: "Average run time, peak memory usage, and CPU core utilization for each major workflow step."
#| echo: false

# Read the summary CSV file generated by our Python script
benchmark_data <- read.csv("benchmark_summary.csv", check.names = FALSE)

# Use the kableExtra package to create a nicely formatted HTML table
knitr::kable(benchmark_data, format = "html")
```

# Assembly Outcome

This table presents the average assembly statistics for each tool across all detected viruses of interest. A higher mapping percentage and larger contigs are generally better.

```{r}
#| label: tbl-assembly
#| tbl-cap: "Average assembly outcome statistics per assembly tool."
#| echo: false

assembly_data <- read.csv("assembly_summary.csv", check.names = FALSE)
knitr::kable(assembly_data, format = "html")
```
# Contig Quality (CheckV)

These tables summarize the total contig counts categorized by CheckV quality scores across all samples. 

## CheckV Quality Categories

```{r}
#| label: tbl-checkv-global
#| tbl-cap: "Total counts of contigs per CheckV-defined quality category across all samples."
#| echo: false

checkv_global_data <- read.csv("checkv_global_summary.csv", check.names = FALSE)
knitr::kable(checkv_global_data, format = "html")
```

## MIUViG Quality Categories

```{r}
#| label: tbl-miuvig-global
#| tbl-cap: "Total counts of contigs per MIUViG-defined quality category across all samples."
#| echo: false

miuvig_global_data <- read.csv("miuvig_global_summary.csv", check.names = FALSE)
knitr::kable(miuvig_global_data, format = "html")
```
