---
title: "LoViMAB Workflow Summary"
format:
  html:
    theme: cosmo
    toc: true
    embed-resources: true
---

# Summary

This report is based on results generated with the LoViMAB v1.0.0 pipeline.

## Table 1. Run Time and Resource Usage

This table shows the average resource usage for key processes across all samples.

```{r}
#| label: tbl-benchmark
#| tbl-cap: "Average run time, peak memory usage, and CPU core utilization for each major workflow step."
#| echo: false

# Read the summary CSV file generated by our Python script
benchmark_data <- read.csv("benchmark_summary.csv", check.names = FALSE)

# Use the kableExtra package to create a nicely formatted HTML table
knitr::kable(benchmark_data, format = "html")
```

# Table 2. Assembly Outcome

This table presents the average assembly statistics for each tool across all detected viruses of interest. A higher mapping percentage and larger contigs are generally better.

```{r}
#| label: tbl-assembly
#| tbl-cap: "Average assembly outcome statistics per assembly tool."
#| echo: false

assembly_data <- read.csv("assembly_summary.csv", check.names = FALSE)
knitr::kable(assembly_data, format = "html")
```